Generating exact lattices in the WFST framework

### 2012-02-02 misc/papers/icassp12_lat/paper.tex
Adding ASRU'11 toolkit paper to repository; making dir for poster
git-svn-id: https://svn.code.sf.net/p/kaldi/code/trunk@641 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8
Final changes to lattice paper; other very minor issues.
git-svn-id: https://svn.code.sf.net/p/kaldi/code/trunk@711 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

% Note: the original submission was rev. 530...
% Template for SLT-2006 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,amssymb,bm,epsfig}
\usepackage{color}
\usepackage{multirow}

@@

\name{ \em Daniel Povey$^1$, Mirko Hannemann$^{1,2}$,  \\
 \em {Gilles Boulianne}$^3$, {Luk\'{a}\v{s} Burget}$^{2,4}$, {Arnab Ghoshal}$^5$, {Milo\v{s} Janda}$^2$, {Martin Karafi\'{a}t}$^2$, {Stefan Kombrink}$^2$, \\
  \em {Petr Motl\'{i}\v{c}ek}$^6$, {Yanmin Qian}$^7$, {Ngoc Thang Vu}$^8$, {Korbinian Riedhammer}$^9$, {Karel Vesel\'{y}}$^2$
    \thanks{Thanks to Honza \v{C}ernock\'{y}, Renata Kohlov\'{a}, and Tom\'{a}\v{s} Ka\v{s}p\'{a}rek for their help relating to the Kaldi'11 workshop at BUT, and to Sanjeev Khudanpur for his help in preparing the paper.  Researchers at BUT were partly supported by Technology Agency of the Czech Republic grant No. TA01011328, Czech Ministry of Education project No. MSM0021630528, and Grant Agency of the Czech Republic project No. 102/08/0707.}}

@@

\begin{abstract}
We describe a lattice generation method that is exact, i.e. it satisfies all the 
natural properties we would want from a lattice of alternative transcriptions of
an utterance.  This method does not introduce substantial overhead above one-best decoding.  Our method is
most directly applicable when using WFST decoders where the WFST is
expanded down to the HMM-state level.  It outputs
lattices that include state-level alignments as well as word labels.
The general idea is to create a state-level lattice during decoding, and to do
a special form of determinization that retains only the best-scoring path
for each word sequence.
\end{abstract}

@@

\section{Introduction}

@@

\section{WFSTs and the decoding problem}
\label{sec:wfst}

The graph creation process we use in our toolkit, Kaldi~\cite{kaldi_paper},
is very close to the standard recipe described in~\cite{wfst},
where the Weighted Finite State Transducer (WFST) decoding graph is
\begin{equation}
  \HCLG = \min(\det(H \circ C \circ L \circ G)),
\end{equation}
where $H$, $C$, $L$ and $G$ represent the HMM structure, phonetic
context-dependency, lexicon and grammar respectively, 
and $\circ$ is WFST composition (note: view $\HCLG$ as a single symbol).
For concreteness we will speak of ``costs'' rather
than weights, where a cost is a floating point number that typically represents a negated
log-probability.  A WFST has a set of states with one distinguished
start state;\footnote{This is the formulation that corresponds best with the toolkit we use.},
each state has a final-cost (or $\infty$ for non-final states);
and there is a set of arcs between the states, where each arc has a weight
(just think of this as a cost for now), an input label and an output
label.  In $\HCLG$, the input labels are the identifiers of context-dependent
HMM states, and the output labels represent words.  For both the input and output
symbols, the special label $\epsilon$ may appear meaning ``no label is present.''

@@

Imagine we want to ``decode'' an utterance of $T$ frames, i.e. we want to
find the most likely word sequence, and the corresponding alignment.  A WFST
interpretation of the decoding problem is as follows.  We construct an
acceptor, or WFSA, as in Fig.~\ref{fig:acceptor} (an acceptor is represented as a
WFST with identical input and output symbols).  It has $T{+}1$ states,
with an arc for each combination of (time, context-dependent HMM state).  The
costs on these arcs are the negated and scaled acoustic log-likelihoods.
Call this acceptor $U$.  Define
\begin{equation}
   S \equiv U \circ \HCLG,
\end{equation}
which is the {\em search graph} for this utterance.  It has approximately $T+1$ times
more states than $\HCLG$ itself.  The decoding problem is equivalent to finding
the best path through $S$.  The input symbol sequence for this best path represents
the state-level alignment, and the output symbol sequence is the corresponding
sentence.  In practice we do not do a full search of $S$, but use beam pruning.
Let $B$ be the searched subset of $S$, containing a subset of the states and arcs
of $S$ obtained by some heuristic pruning procedure.  
When we do Viterbi decoding with beam-pruning, we are finding the best path through $B$. 
%
Since the beam pruning is a part of any practical search procedure and cannot
easily be avoided, we will define the desired outcome of lattice generation in terms
of the visited subset $B$ of the search graph $S$.

\section{The lattice generation problem}
\label{sec:lattices}

There is no generally accepted single definition of a lattice.  In~\cite{efficient_general}
and~\cite{sak2010fly}, it is defined as a labeled, weighted, directed acyclic graph
(i.e. a WFSA, with word labels).  In~\cite{ney_word_graph}, time information
is also included.  In the HTK lattice format~\cite{htkbook}, phone-level time alignments 
are also supported (along with separate language model, acoustic and pronunciation-probability 
scores), and in~\cite{saon2005anatomy}, state-level alignments are also produced.
In our work here we will be producing state-level alignments; in fact, the input-symbols
on our graph, which we call {\em transition-ids}, are slightly more fine-grained
than acoustic states and contain sufficient information to reconstruct the phone
sequence.

@@

\section{Previous lattice generation methods}
\label{sec:previous}

Lattice generation algorithms tend to be closely linked to particular types of decoder,
but are often justified by the same kinds of ideas.
A common assumption underlying lattice generation methods is the {\em word-pair assumption}
of~\cite{ney_word_graph}.  This is the notion that the time boundary between a pair of words
is not affected by the identity of any earlier words.  In a decoder in which there is
a different copy of the lexical tree for each preceding word, 
assuming the word-pair assumption holds, in order to generate an accurate lattice, it is
sufficient to store a single Viterbi back-pointer at the word level; the entire set of
such back-pointers contains enough information to generate the lattice.  Authors who have used
this type of lattice generation method~\cite{ney_word_graph,odell_thesis} have generally
not been able to evaluate how correct the word-pair assumption is in practice, but it seems
unlikely to cause problems.  Such methods are not applicable for us anyway, as we
use a WFST based decoder in which each copy of the lexical tree does not have a unique
one-word history.

@@

\section{Overview of our algorithm}
\label{sec:overview}

\subsection{Version without alignments}

@@

After the determinization phase, we prune again using the beam $\alpha$.  This is needed because
the determinization process can introduce a lot of unlikely arcs.  In fact, for particular
utterances, the determinization process can cause the lattice to expand enough to
exhaust memory.  To deal with this, we currently just detect when determinization
has produced more than a pre-set maximum number of states, then we prune with a tighter
beam and try again.  In future, we may try more sophisticated methods such as a
determinization algorithm that does pruning itself.

@@

\subsection{Keeping separate graph and acoustic costs}

@@

Formally, if each weight is a pair $(a,b)$, then $(a,b) \otimes (c,d) = (a{+}c, b{+}d)$,
and $(a,b) \oplus (c,d)$ is equal to $(a,b)$ if $a{+}b < c{+}d$ or if $a{+}b = c{+}d$ and $a{-}b < c{-}d$,
and otherwise is equal to $(c,d)$.  This is equivalent to the lexicographic semiring 
of~\cite{roark2011lexicographic}, on the pair $((a{+}b),(a{-}b))$.

\subsection{Keeping state-level alignments}

@@

\subsection{Summary of our algorithm}

We now summarize the lattice generation algorithm.  During decoding, we create a data-structure
corresponding to a full state-level lattice.  That is, for every arc of $\HCLG$, we traverse
on every frame, we create a separate arc in the state-level lattice.  These arcs
contain the acoustic and graph costs separately.  We prune the state-level graph using
a beam $\alpha$; we do this periodically (every 25 frames) but this is equivalent to
doing it just once at the end, as in~\cite{efficient_general}.  Let the 
final pruned state-level lattice be $P$.

Let $Q = \inv(P)$, and let $E$ be an encoded version of $Q$ as described above (with the
state labels as part of the weights).  The final lattice is
\begin{equation}
   L = \mathrm{prune}(\mathrm{det}(\mathrm{rmeps}(E)), \alpha) .
\end{equation}
The determinization and epsilon removal are done together by a single algorithm
that we will describe below.  $L$ is a deterministic, acyclic weighted acceptor with the 
words as the labels, and the graph and acoustic costs and the alignments
encoded into the weights.  The costs and alignments are not ``synchronized'' 
with the words.

\section{Details of our determinization algorithm}
\label{sec:details}

@@

@@

\section{Experimental results}
\label{sec:exp}

We report experimental results on the Wall Street Journal database of
read speech.  
Our system is a standard mixture-of-Gaussians system trained on the SI-284
training data; we test on the November 1992 evaluation data.  
For these experiments, we generate lattices with the bigram language model
supplied with the WSJ database, and for rescoring experiments we
use the trigram language model.  The acoustic scale was $1/16$ for first-pass
decoding and $1/15$ for LM rescoring.  
For simplicity, we used a decoder that
does not support a ``maximum active states'' option, so the only variables
to consider are the beam used in the Viterbi beam search, and the separate
beam $\alpha$ used for lattice generation.

\begin{figure}
\centering
   \includegraphics[width=0.9\columnwidth]{figures/latbeam.eps} 
 \vspace*{-0.1in}

   \caption{\vspace*{-0.2in} Varying lattice beam $\alpha$ (Viterbi pruning beam fixed at 15) }
  \vspace{-0.08in}
  \label{fig:latbeam}
\end{figure}

Figure~\ref{fig:latbeam} shows how various quantities change as we vary
$\alpha$, with the Viterbi beam fixed at 15.  Note that we get all the improvement from
LM rescoring by increasing $\alpha$ to 4.  The time taken by our algorithm started to increase rapidly after about
$\alpha=8$, so a value of $\alpha$ anywhere between about 4 and 8 is sufficient for LM rescoring 
and still does not slow down decoding too much.  We do not display the real-time factor of the non-lattice-generating
decoder on this data (2.26) as it was actually slower than the lattice generating decoder; this is
presumably due to the overhead of reference counting.
Out of vocabularly words (OOVs) provide a floor on the lattice oracle error rate:
of 333 test utterances, 87 contained at least one OOV word, yet only 93 sentences (6 more) had oracle errors
with $\alpha=10$.  Lattice density is defined as the average number of arcs crossing each frame.
Figure~\ref{fig:viterbibeam} shows the effect of varying the
Viterbi decoding beam, while leaving $\alpha$ fixed at 7.

\begin{figure}
\centering
   \includegraphics[width=0.9\columnwidth]{figures/decodebeam.eps} 
 \vspace*{-0.1in}
    \caption{\vspace*{-0.2in} Varying Viterbi pruning beam (lattice beam $\alpha$ fixed at 7) }
  \label{fig:viterbibeam}
  \vspace{-0.08in}
\end{figure}

%\vspace*{-0.075in}
\section{Conclusions}
\label{sec:conc}
%\vspace*{-0.05in}

We have described a lattice generation method that is to our knowledge the first
efficient method not to rely on the word-pair assumption of~\cite{ney_word_graph}.
It includes an ingenious way of obtaining state-level alignment information
via determinization in a specially designed semiring.

%\vspace*{-0.1in}
\bibliographystyle{IEEEbib}
\bibliography{refs}

>>>>

% paper # 3887, pw CF8FECE1
% Note: the original submission was rev. 530... 
% submitted again at 539 before review..
% Template for SLT-2006 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,amssymb,bm,epsfig}
\usepackage{color}
\usepackage{multirow}

@@

\name{ \em Daniel Povey$^1$, Mirko Hannemann$^{1,2}$,  \\
 \em {Gilles Boulianne}$^3$, {Luk\'{a}\v{s} Burget}$^{2,4}$, {Arnab Ghoshal}$^5$, {Milo\v{s} Janda}$^2$, {Martin Karafi\'{a}t}$^2$, {Stefan Kombrink}$^2$, \\
  \em {Petr Motl\'{i}\v{c}ek}$^6$, {Yanmin Qian}$^7$, {Korbinian Riedhammer}$^9$, {Karel Vesel\'{y}}$^2$, {Ngoc Thang Vu}$^8$
    \thanks{Thanks to Honza \v{C}ernock\'{y}, Renata Kohlov\'{a}, and Tom\'{a}\v{s} Ka\v{s}p\'{a}rek for their help relating to the Kaldi'11 workshop at BUT, and to Sanjeev Khudanpur for his help in preparing the paper.  Researchers at BUT were partly supported by Technology Agency of the Czech Republic grant No. TA01011328, Czech Ministry of Education project No. MSM0021630528, and Grant Agency of the Czech Republic project No. 102/08/0707.  Arnab Ghoshal was supported by EC FP7 grant 213850 (SCALE), and by EPSRC grant EP/I031022/1 (NST).}}

@@

\begin{abstract}
We describe a lattice generation method that is exact, i.e. it satisfies all the 
natural properties we would want from a lattice of alternative transcriptions of
an utterance.  This method does not introduce substantial overhead above one-best decoding.  Our method is
most directly applicable when using WFST decoders where the WFST is
``fully expanded'', i.e. where the arcs correspond to HMM transitions.  It outputs
lattices that include HMM-state-level alignments as well as word labels.
The general idea is to create a state-level lattice during decoding, and to do
a special form of determinization that retains only the best-scoring path
for each word sequence.  
This special determinization algorithm is a solution to the following problem:
Given a WFST A, compute a WFST B that, for each input-symbol-sequence of A,
contains just the lowest-cost path through A.
\end{abstract}

@@

\vspace*{-0.075in}
\section{Introduction}
\vspace*{-0.05in}

@@

\vspace*{-0.075in}
\section{WFSTs and the decoding problem}
\vspace*{-0.05in}
\label{sec:wfst}

The graph creation process we use in our toolkit, Kaldi~\cite{kaldi_paper},
is very close to the standard recipe described in~\cite{wfst},
where the Weighted Finite State Transducer (WFST) decoding graph is
\begin{equation}
  \HCLG = \min(\det(H \circ C \circ L \circ G)),
\end{equation}
where $H$, $C$, $L$ and $G$ represent the HMM structure, phonetic
context-dependency, lexicon and grammar respectively, 
and $\circ$ is WFST composition (note: view $\HCLG$ as a single symbol).
For concreteness we will speak of ``costs'' rather
than weights, where a cost is a floating point number that typically represents a negated
log-probability.  A WFST has a set of states with one distinguished
start state\footnote{This is the formulation that corresponds best with the toolkit we use.};
each state has a final-cost (or $\infty$ for non-final states);
and there is a set of arcs between the states, where each arc has an
input label, an output label, and a weight
(just think of this as a cost for now).
In $\HCLG$, the input labels are the identifiers of context-dependent
HMM states, and the output labels represent words.  For both the input and output
labels, the special symbol $\epsilon$ may appear, meaning ``no label is present.''

@@

Imagine we want to ``decode'' an utterance of $T$ frames, i.e. we want to
find the most likely word sequence and its corresponding state-level alignment.  A WFST
interpretation of the decoding problem is as follows.  We construct an
acceptor, or WFSA, as in Fig.~\ref{fig:acceptor} (an acceptor is represented as a
WFST with identical input and output symbols).  It has $T{+}1$ states,
with an arc for each combination of (time, context-dependent HMM state).  The
costs on these arcs correspond to negated and scaled acoustic log-likelihoods.
Call this acceptor $U$.  Define
\begin{equation}
   S \equiv U \circ \HCLG,
\end{equation}
which we call the {\em search graph} of the utterance.  It has approximately $T{+}1$ times
more states than $\HCLG$ itself.  The decoding problem is equivalent to finding
the best path through $S$.  The input symbol sequence for this best path represents
the state-level alignment, and the output symbol sequence is the corresponding
sentence.  In practice we do not do a full search of $S$, but use beam pruning.
Let $B$ be the searched subset of $S$, containing a subset of the states and arcs
of $S$ obtained by some heuristic pruning procedure.  
When we do Viterbi decoding with beam-pruning, we are finding the best path through $B$. 
%
Since the beam pruning is a part of any practical search procedure and cannot
easily be avoided, we will define the desired outcome of lattice generation in terms
of the visited subset $B$ of $S$.

\vspace*{-0.075in}
\section{The lattice generation problem}
\vspace*{-0.05in}
\label{sec:lattices}

There is no generally accepted single definition of a lattice.  In~\cite{efficient_general}
and~\cite{sak2010fly}, it is defined as a labeled, weighted, directed acyclic graph
(i.e. a WFSA, with word labels).  In~\cite{ney_word_graph}, time information
is also included.  In the HTK lattice format~\cite{htkbook}, phone-level time alignments 
are also supported (along with separate language model, acoustic and pronunciation-probability 
scores), and in~\cite{saon2005anatomy}, HMM-state-level alignments are also produced.
In our work here we will be producing state-level alignments; in fact, the input-symbols
on our graph, which we call {\em transition-ids}, are slightly more fine-grained
than acoustic states and contain sufficient information to reconstruct the phone
sequence.

@@

\vspace*{-0.075in}
\section{Previous lattice generation methods}
\vspace*{-0.05in}
\label{sec:previous}

Lattice generation algorithms tend to be closely linked to particular types of decoder,
but are often justified by the same kinds of ideas.
A common assumption underlying lattice generation methods is the {\em word-pair assumption}
of~\cite{ney_word_graph}.  This is the notion that the time boundary between a pair of words
is not affected by the identity of any earlier words.  In a decoder in which there is
a different copy of the lexical tree for each preceding word, 
assuming the word-pair assumption holds, in order to generate an accurate lattice, it is
sufficient to store a single Viterbi back-pointer at the word level; the entire set of
such back-pointers contains enough information to generate the lattice.  Authors who have used
this type of lattice generation method~\cite{ney_word_graph,odell_thesis} have generally
not been able to evaluate how correct the word-pair assumption is in practice, but it seems
unlikely to cause problems.  Such methods are not applicable for WFST based decoders anyway.

@@

\vspace*{-0.075in}
\section{Overview of our algorithm}
\vspace*{-0.05in}
\label{sec:overview}

\subsection{Version without alignments}
\vspace*{-0.05in}

@@

After the determinization phase, we prune again using the beam $\alpha$.  This is needed because
the determinization process can introduce a lot of unlikely arcs.  In fact, for particular
utterances, the determinization process can cause the lattice to expand enough to
exhaust memory.  To deal with this, we currently just detect when determinization
has produced more than a pre-set maximum number of states, then we prune with a tighter
beam and try again.

@@

\vspace*{-0.075in}
\subsection{Keeping separate graph and acoustic costs}
\vspace*{-0.05in}

@@

Formally, if each weight is a pair $(a,b)$, then $(a,b) \otimes (c,d) = (a{+}c, b{+}d)$,
and $(a,b) \oplus (c,d)$ is equal to $(a,b)$ if $a{+}b < c{+}d$ or if $a{+}b = c{+}d$ and $a{-}b < c{-}d$,
and otherwise is equal to $(c,d)$.  This is equivalent to the normal lexicographic semiring (see~\cite{roark2011lexicographic}) on the pair $((a{+}b),(a{-}b))$.

\vspace*{-0.075in}
\subsection{Keeping state-level alignments}
\vspace*{-0.05in}

@@

\vspace*{-0.075in}
\subsection{Summary of our algorithm}
\vspace*{-0.05in}

During decoding, we create a data-structure
corresponding to a full state-level lattice.  That is, for every arc of $\HCLG$, we traverse
on every frame, we create a separate arc in the state-level lattice.  These arcs
contain the acoustic and graph costs separately.  We prune the state-level graph using
a beam $\alpha$; we do this periodically (every 25 frames) but this is equivalent to
doing it just once at the end, as in~\cite{efficient_general}.  Let the 
final pruned state-level lattice be $P$.
Let $Q = \inv(P)$, and let $E$ be an encoded version of $Q$ as described above (with the
state labels as part of the weights).  The final lattice is
\vspace*{-0.075in}
\begin{equation}
   L = \mathrm{prune}(\mathrm{det}(\mathrm{rmeps}(E)), \alpha) . \vspace*{-0.075in}
\end{equation}
The determinization and epsilon removal are done together by a single algorithm
that we will describe below.  $L$ is a deterministic, acyclic weighted acceptor with the 
words as the labels, and the graph and acoustic costs and the alignments
encoded into the weights.  The costs and alignments are not ``synchronized'' 
with the words.

\vspace*{-0.075in}
\section{Details of our determinization algorithm}
\vspace*{-0.05in}
\label{sec:details}

@@

%Although we have not written a proof of correctness of this algorithm, we
%have tested it thoroughly.  This is done by generating random WFSTS,
%applying this algorithm, and if it terminates, checking that the result
%is deterministic and is equivalent (in this semiring) to the original WFST
%represented as an acceptor in this semiring.

Since submitting this paper, we have become aware of~\cite{shafran2011efficient},
which solves the exact same problem for a different purpose.  They use a semiring
which is more complicated than ours (the string part of the semiring becomes a
structured object with parentheses).  They use this semiring instead of the one
 we describe here, because in our semiring the $\oplus$-sum of two weights 
does not necessarily left-divide the weights, and this is a problem for 
a typical determinization algorithm.  We bypass
this problem by defining a ``common divisor'' operation $\boxplus$ with the
right properties (it $\oplus$-adds the weight part and returns the longest
common prefix of the string part).  We use this instead of
$\oplus$ when finding divisors in the determinization algorithm.

@@

\vspace*{-0.1in}
\section{Experimental results}
\vspace*{-0.075in}
\label{sec:exp}

We do not compare with any other algorithms,
as~\cite{ney_word_graph,odell_thesis,efficient_general} are designed for
different types of decoders than ours, and the lattices contain less information,
making comparisons hard to interpret; the algorithm of~\cite{saon2005anatomy} has
similar requirements and outputs as ours, but besides being inexact, it is bound
to be slower due to the need to store $N$ back-pointers, so we did not view it as
worthwhile to do the experiment.

We report experimental results on the Wall Street Journal database of
read speech. 
Our system is a standard mixture-of-Gaussians system trained on the SI-284
training data; we test on the November 1992 evaluation data.  
We generated lattices with the bigram language model
supplied with the WSJ database, and for rescoring experiments we
use the trigram language model.  The acoustic scale was $1/16$ for first-pass
decoding and $1/15$ for LM rescoring.  
For simplicity, we used a decoder that
does not support a ``maximum active states'' option, so the only variables
to consider are the beam used in the Viterbi beam search, and the separate
beam $\alpha$ used for lattice generation.

\begin{figure}[t]
\centering
   \includegraphics[width=0.9\columnwidth]{figures/latbeam.eps} 
 \vspace*{-0.1in}

   \caption{ { Lattice properties, varying lattice beam $\alpha$ (Viterbi pruning beam fixed at 15)} }
  \vspace{-0.15in}
  \label{fig:latbeam}
\end{figure}

Figure~\ref{fig:latbeam} shows how the lattice properties change as we vary
$\alpha$, with the Viterbi beam fixed at 15; Figure~\ref{fig:viterbibeam} varies
the Viterbi decoding beam, leaving $\alpha$ fixed at 7.  Lattice density is
defined as the average number of arcs crossing each frame.  We get all the
improvement from LM rescoring by increasing $\alpha$ to 4, and time taken
increases rapidly when $\alpha > 8$, so we recommend roughly $4 < \alpha < 8$ for
LM rescoring purposes.  We do not display the real-time factor of the
non-lattice-generating decoder on this data (2.26xRT) as it was actually slower
than the lattice generating decoder; this is possibly due to the overhead of
reference counting.  Out of vocabularly words (OOVs) provide a floor on the
lattice oracle error rate: of 333 test utterances, 87 contained at least one OOV
word, yet only 93 sentences (6 more) had oracle errors with $\alpha=10$.

\begin{figure}[t]
\centering
   \includegraphics[width=0.9\columnwidth]{figures/decodebeam.eps} 
 \vspace*{-0.1in}
    \caption{ {Lattice properties, varying Viterbi pruning beam (lattice beam $\alpha$ fixed at 7)}}
  \label{fig:viterbibeam}
  \vspace{-0.15in}
\end{figure}

\vspace*{-0.1in}
\section{Conclusions}
\label{sec:conc}
\vspace*{-0.075in}

We have described a lattice generation method that is to our knowledge the first
efficient method that does not rely on the word-pair assumption of~\cite{ney_word_graph}.
It includes an ingenious way of obtaining HMM-state-level alignment information
via determinization in a specially designed semiring.

\vspace*{-0.04in}
\footnotesize {
\vspace*{-0.1in}
\bibliographystyle{IEEEbib}
\bibliography{refs}
}
